### 2017-04-03 paper/evaluation.tex
added missing fix
wip - rq3

\begin{itemize}
\item Potential
  \begin{itemize}
  \item \textbf{\numRQA.} \RQA
  \item \textbf{\numRQB.} \RQB    
  \end{itemize}
\item Effectiveness
  \begin{itemize}
  \item \textbf{\numRQD.} \RQD
  \end{itemize}  
\item Adoption
  \begin{itemize}
  \item \textbf{\numRQC.} \RQC    
  \item \textbf{\numRQE.} \RQE
  \end{itemize}
\item Tradeoff
  \begin{itemize}
  \item \textbf{\numRQF.} \RQF    
  \end{itemize}          
\end{itemize}

@@

Prior to running this script, we inspected Maven execution logs from a
sample inclduing a hundred projects.  The goal of this inspection step
is to find tasks unrelated to testing (\eg, \emph{javadoc} generation
and static analyses) that could interfere in our measurements.  The
tasks we found were ignored from execution (lines 1-3).  Furthermore,
to avoid noise from operating system events, we configured our
workstation to run only essential services.  The machine was dedicated
to our experiments and we accessed it via SSH. In addition, we
configured the \CodeIn{isolcpus} option from the Linux Kernel
\cite{linux-kernel} to isolate six virtual CPUs to execute our
experiment, leaving the remaining CPUs to run OS
processes~\cite{isolcpus-use}.  The rationale for this decision is to
prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared the sequential execution of tests
using Maven with JUnit's default \CodeIn{JUnitCore} runner, invoked
from the command line.  We observed that results were very similar.

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{} group), tests that run in one to five minutes (\medg{}
group), and tests that run in five or more minutes (\longg{}
group). We followed a similar methodology to group projects by time as
Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
regression test selection.\Comment{ and added the \medg{} group due to
  the variability of the time cost from subjects out of the \shortg{}
  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As it is to be expected, \longg{} and \medg{} projects do
not occur as frequently as \shortg{} projects.  However, they do ocur
in relatively high numbers.  Figure~\ref{fig:rq1-boxplot} shows cost
distribution of test suites in each group as boxplots.  The
distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
  group}.  The test suites in this group run in 15 or less seconds for
over 75\% of the cases.  Such scenarios constitute the majority of the
cases we analyzed.  Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers (dots) in the plot.

@@

\vspace{1ex}
\begin{itemize}
    \item \textbf{\RQB}
\end{itemize}

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, parallelism by itself does
not assure speedups on those projects.  One sensible factor that is
important to the effectiveness of low-level parallelism is the
distribution of test costs in the test suite.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.15\textwidth}
      \centering
      \includegraphics[width=.85\textwidth]{plots/boxplots-testcases.pdf}
        \caption{\label{fig:medtcost}Distribution of test cases.}
    \end{subfigure}~
    \begin{subfigure}{0.3\textwidth}
      \centering
      \includegraphics[width=.95\textwidth]{plots/scatter-testcost.pdf}
        \caption{\label{fig:scattercost}\Fix{legend}}
     \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  7 & 15 & 12 \\
        Medium & 22 & 19 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}Standard deviantion of test cases}
    \end{subfigure}%
    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}%
\end{figure}

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of tests per project.  We observed that the average
median value of execution cost for a test was relatively small (dashed
horizontal red lines), namely 0.31s for \medg{} projects and
0.23s for \longg{} projects.  Note that correlation between cost
of test suites and cost of their individual tests is not to be
expected.  The standard deviation ($\sigma$) associated with each
distribution was relatively low.  Figure~\ref{fig:sd} shows the number
of projects within specific ranges of $\sigma$ values.  We also
observed that projects with very high standard deviations may or may
not be indicative of monopolization of execution by a small number of
tests.  For example, the highest value of $\sigma$ occurred in project
\CodeIn{uber\_chaperone}, whose test suite was classified as
medium-running.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{uber\_chaperone} was an extreme case;
we did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119} take more than
\Fix{1s} to run.

@@

%% \Jbc{I shouldn't introduce parallelization arguments here but we have
%% to address this at some point:
%% Regression tests that are well distributed may benefit from
%% parallelism since more tests executes at the same time while the
%% opposite scenario may require a different approach. In the later
%% scenario, executing tests in parallel may have insignificant impact
%% since a small subset of test cases dominates the execution.}

@@

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default, and
compared their time cost with sequential execution. We are interested
in measuring the execution speedup (if any) when the parallelization
settings are activated.

@@

>>>>

\begin{itemize}
\item Potential
  \begin{itemize}
  \item \textbf{\numRQA.} \RQA
  \item \textbf{\numRQB.} \RQB    
  \end{itemize}
\item Effectiveness
  \begin{itemize}
  \item \textbf{\numRQD.} \RQD
  \end{itemize}  
\item Adoption
  \begin{itemize}
  \item \textbf{\numRQC.} \RQC    
  \item \textbf{\numRQE.} \RQE
  \end{itemize}
\item Tradeoffs
  \begin{itemize}
  \item \textbf{\numRQF.} \RQF    
  \end{itemize}          
\end{itemize}

@@

Prior to running this script, we inspected Maven execution logs from a
sample including a hundred projects.  The goal of this inspection step
is to find tasks unrelated to testing (\eg, \emph{javadoc} generation
and static analyses) that could interfere in our measurements.  The
tasks we found were ignored from execution (lines 1-3).  Furthermore,
to avoid noise from operating system events, we configured our
workstation to run only essential services.  The machine was dedicated
to our experiments and we accessed it via SSH. In addition, we
configured the \CodeIn{isolcpus} option from the Linux Kernel
\cite{linux-kernel} to isolate six virtual CPUs to execute our
experiment, leaving the remaining CPUs to run OS
processes~\cite{isolcpus-use}.  The rationale for this decision is to
prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared the sequential execution of tests
using Maven with JUnit's default \CodeIn{JUnitCore} runner, invoked
from the command line.  We observed that results were very similar.

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{} group), tests that run in one to five minutes (\medg{}
group), and tests that run in five or more minutes (\longg{}
group). We followed a similar methodology to group projects by time as
Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
regression test selection.\Comment{ and added the \medg{} group due to
  the variability of the time cost from subjects out of the \shortg{}
  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As it is to be expected, \longg{} and \medg{} projects do
not occur as frequently as \shortg{} projects.  However, they do occur
in relatively high numbers.  Figure~\ref{fig:rq1-boxplot} shows cost
distribution of test suites in each group as boxplots.  The
distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
  group}.  The test suites in this group run in 15 or less seconds for
over 75\% of the cases.  Such scenarios constitute the majority of the
cases we analyzed.  Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers (dots) in the plot.

@@

\vspace{1ex}
\begin{itemize}
    \item \numRQB. \textbf{\RQB}
\end{itemize}

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  This reveals the importance to
speedup test execution not only to huge projects as those from
Google~\cite{google-tap,google-ci} and
Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.  However, use of
parallelism does not imply speedups.  One sensible factor that is
important to the effectiveness of low-level parallelism is the
distribution of test costs in the test suite.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

\begin{figure}[t]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions.}%
\end{figure}

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  Note that high standard
deviations may or may not be indicative of monopolization of execution
by a small number of tests.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
medium group.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} of the execution cost is dominated by only \Fix{3\%}
of the tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{uber\_chaperone} was an extreme
case.  We did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119 (23\%)} take more
than \Fix{1s} to run.

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.15\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{plots/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}Size of test suites.}
  \end{subfigure}
  ~
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=.95\textwidth]{plots/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}Size versus running time of
      test suites.}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}Relating size and time.}%
\end{figure}

Figure~\ref{fig:time-distributions} showed that the average median
times were similar.  A closer inspection on results indicates that the
difference in overall running times across projects in these groups is
mainly justified by the number of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.\Mar{$\leftarrow$ show
  stats to indicate discrimination of two distributions} Furthermore,
we also noted a strong positive correlation between running time and
number of test on projects in the \longg{} group.  The positive
correlation between these two variables was, however, weak in the
\medg{} group, suggesting that saving time in this group with test
suite parallelization may be more challenging as relatively fewer
tests dominate overall execution time.  Figure~\ref{fig:scattercost}
shows these results.

%% This 
%% indication that it is more beneficial to parallelize long projects as
%% cost is spread across many

@@

%% Regression tests that are well distributed may benefit from
%% parallelism since more tests executes at the same time while the
%% opposite scenario may require a different approach. In the later
%% scenario, executing tests in parallel may have insignificant impact
%% since a small subset of test cases dominates the execution.}

@@

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}), and compared their time cost with sequential
execution. We are interested in measuring the execution speedup (if
any) when the parallelization settings are activated.

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive
%%  LocalWords:  linkbench
